% !TEX root =  Main.tex
\chapter{Change Log}
Changes in Bold were required by the Graduate School

\section{Changes in v1.16}
\begin{itemize}
\item{\bfseries Added University of Maine Graduate School Land Acknowledgment}
\end{itemize}

\section{Changes in v1.15}
\begin{itemize}
\item{\bfseries Add “APPENDICES” to title of first Appendix and TOC when multiple appendices are present.}
\end{itemize}

\section{Changes in v1.14}
\begin{itemize}
\item{\bfseries Ensured double spacing in chapter titles.}
\item{\bfseries Removed extra space above chapter titles.}
\item{{\bfseries Removed extra space between chapters in list of figures and list of tables.} This is implemented as an option, you can add the space back (for unofficial copies) with the loftspacing option.}
\item{\bfseries Changed ``The University of Maine'' to ``the University of Maine'' in the auto-sentence of the author biography.}
\item{\bfseries Reduce space between title and author name on abstract pages.}
\item{\bfseries Remove “Chapter” heading from TOC.}
\item{Fixed problem with link target (when using hyperref) and page number in TOC for reference section.}
\item{\bfseries changed ``The University of Maine'' to ``the University of Maine'' in the auto-sentence of the author biography.}
\item{Improved capitalization enforcement for chapter headings and TOC entries.  This should make redefining section names (as when using babel) much easier.}
\item{Dropped 2-volume support. (Graduate School no longer needs a printed copy of the thesis.)}
\item{Page number placement now controlled by a class option.  It's also more consistent in its application as a result.}
\item{\bfseries Extra space before ``Chapter'' label in TOC has been removed.}
\item{``Chapter'' and ``Appendix'' in chapter headings is now printed in all uppercase.}
\item{\bfseries Tweaks to make 5-dot minimum in TOC leaders better respected.  Thanks to pmbean6 for this fix.}
\item{\bfseries Use a pronoun instead of author name for the last sentence of author biography.  Users now need to define their preferred pronoun with the \verb=\authorpronoun= command.  Do not forget to capitalize the first letter of the pronoun.  If no pronoun is provided, then the full author name will appear in the last sentence of the biography.}
\item{\bfseries When figure/table captions are too long to go into the table of contents, the graduate school wants the entry in the table of contents to match the first sentence of caption exactly.  To facilitate this the \verb=\caption= command has been redefined so that the optional argument, if given, is automatically prepended to the caption text.  Older theses, for which this new behavior would be undesirable, can turn it off with the legacycaptions option.}
\item{\bfseries On title page, when the name and title of an advisor or committee member is long enough to wrap to a second line, that second line will be indented 1.5em (the same as the indentation of a paragraph in the body of the thesis).}
\end{itemize}

\section{Changes in v1.13}
\begin{itemize}
\item{Short form of advisor's name can now be entered as an optional argument of \verb=\principaladvisor=.}
\item{Bugfix: idecimal and jdecimal heading styles were suppressing the section numbers.  Thanks to pmbean6 for this fix.}
\item{Margin widths have been tweaked a little so that they more closely conform to the guidelines.  Thanks to pmbean6 for this fix.}
\item{If you edited the class file to get justified text back, then subsection headings were being indented in jdecimal style.  This has been fixed in preparation for later changes.  Thanks to pmbean6 for this fix.}
\item{Package conflict with float package has been resolved.  Thanks to pmbean6 for this fix.  Those updating thesis should change listof environments to thesislist.}
\item{Bugfix: The default setting of \verb=\parindent= was being forced to 0, which was not as intended.}
\item{Indentation for the headings has been decoupled from \verb=\parindent= and is now tied to \verb=\headindent=.}
\item{Added some basic metadata (title and author) handling when hyperref is loaded.  Thanks to pmbean6 for this enhancement}
\item{\bfseries Adjusted page numbering to account for removal of Dissertation Acceptance page.}
\end{itemize}

\section{Changes in v1.12}
\begin{itemize}
\item{\bfseries Eliminated Dissertation Acceptance and Library Rights Statement pages.}
\end{itemize}

\section{Changes in v1.11}
\begin{itemize}
\item{\bfseries Replaced ``thesis'' with \verb=\@type= on Library Rights page.}
\item{\textbf{Labels for signature lines now use the same size font as the rest of the thesis (they were formerly reduced).}}
\item{\textbf{Gap between the title and the text on Dissertation Acceptance and Library Rights page has been reduced.}}
\item{\textbf{Mandatory sentence at the end of the Author Biography (and which the class file produces automatically) is no longer its own paragraph.}}
\item{\textbf{The default headings system has been modified to make it match more closely with the justified decimal example in the Guidelines.}}
\item{Two additional headings systems (headings and idecimal) have been added.  These are based on the headings and indented decimal examples in the Guidelines.}
\item{\bfseries Improved Widow/Orphan protection in the TOC.}
\item{\bfseries Improved Widow/Orphan protection in bibliography.}
\end{itemize}

\section{Changes in v1.10}
\begin{itemize}
\item{\textbf{Alignment of multi-line table of contents entries for Appendices altered}}
\item{5-dot leader minimum code reworked to be more robust}
\end{itemize}

\section{Changes in v1.9}
\begin{itemize}
\item{\textbf{Acceptance Page title consolidated to a single line.}}
\item{\textbf{Removed ``Submitted for graduation\ldots'' from Acceptance Page.}}
\end{itemize}

\section{Changes in v1.8}
\begin{itemize}
\item{\textbf{Hyphenation disabled.}}
\item{\textbf{Full justification disabled.}}
\end{itemize}

\section{Changes in v1.7}
\begin{itemize}
\item{Added \verb=\highlight= command.}
\item{Modifications to \verb=\pocket= to make its ToC entries match other chapter-level entries.}
\item{Added two-volume support.}
\item{Made some modifications to help with widow/orphan control in the ToC.}
\end{itemize}

\section{Changes in v1.6}
\begin{itemize}
\item{\textbf{Changed line length for multiple line entires in the ToC.}}
\item{\textbf{Removed the multiple appendices ``Appendices'' header from the ToC.}}
\item{Added twoside option.}
\item{Added unbound option.}
\item{Added hooks to alter heading styles.}
\item{Added chicago and apa option to switch headings automatically to the appropriate style.}
\end{itemize}

\section{Changes in v1.5}
\begin{itemize}
\item{License Changed to LPPL v1.3c.}
\item{Generalized Dissertation Acceptance Page.}
\item{Changed to signature line on Library Rights Page.}
\item{Fixed delimiter in figure and table captions.}
\item{Unified \verb=\copyrightyear{...}= and \verb=\copyrightpage= into single command.}
\item{Refined support for two advisors and number of committee members.}
\item{Removed support for External Reader on title page.}
\item{Created patch code to fix list of tables and list of figures when hyperref is used.}
\item{Added layabstract environment.}
\item{Added listof environment.}
\item{Changed font for verbatim environment and \verb=\verb= command.}
\item{Fixed typesetting of dedication.}
\item{General file maintenance.}
\item{Added insertion of ``Appendices'' to ToC when there are multiple appendices.}
\item{Modified biography environment to auto-generate the last sentence.}
\item{Made identification of number of advisors and committee members automatic.}
\item{Removed \verb=\appsection{...}= as it is redundant with \verb=\section*{...}=.}
\item{Changed way ``Chapters'' and ``Appendices'' are added to the TOC.}
\item{Added tocvsec2 dependance to make the change in TOC depth for the front matter and appendices automatic.}
\item{Modified preface environment to make the non-numbering of its sections, subsections, etc automatic.}
\item{Reserved \verb=\part= for multiple volume support.}
\item{Added \verb=\pocket=.}
\item{Defined a pseudo \verb=\texorpdfstring= command for use in chapter titles.  When hyperref is loaded (and defines the command properly) this has the effect of hiding \verb=\MakeUppercase= commands from hyperref.}
\item{Made Preface, Dedication, and Acknowledgements double spaced.}
\item{Created type variables and commands that allows switching to ``thesis'' or ``project'' instead of ``dissertation.''}
\item{Removed footnote rule.}
\item{Renamed \verb=\labelchaptersintoc= to \verb=\toclabel=, generalized its function, and made it compatible with hyperref.}
\item{Added commands to compress title page when needed.}
\end{itemize}

\section{Changes prior to v1.5}
This list is not entirely complete but is a best reconstruction as I can manage.  Changes were not logged prior to v1.5.
\begin{itemize}
\item{Added Dissertation Acceptance Page}
\item{Added support for 6 member committees}
\item{Removed Boldface from TOC entries}
\item{Reduced size of chapter and section headers to match text font, both in place and TOC entries}
\item{Added support for two advisors}

\end{itemize}

\endinput