% !TEX root =  Main.tex
\chapter{Front.tex}

The front matter of your thesis is primarily made up of special things that are required by the Graduate School, but also contains some optional elements.  Table \ref{front} provides a summary of these elements.

\begin{table}
\begin{minipage}{\textwidth}
\centering
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
\hline\hline
Thesis Element & Required or Optional\\
\hline
Copyright Page & Optional\\
Abstract & Required\\
Lay Abstract & Special\footnote{See section \ref{abstracts}}\\
Preface & Optional\\
Dedication & Optional\\
Acknowledgements & Optional\\
Table of Contents & Required\\
\hline\hline
\end{tabular*}\\
\end{minipage}
\caption{The elements of the front matter for your thesis.}
\label{front}
\end{table}

\section{Copyright}\label{copy}

\begin{verbatim}
\copyrightpage[copyright holder]{year}
\end{verbatim}

This command creates a copyright page.  This page is optional (unless you've taken the time to register the copyright, in which case it's required by law, not the Graduate School), so you can neglect this page if you want to.  If you do issue it, there are a pair of arguments that it takes.  The first (between ``['' and ``]'') specifies the copyright holder.  This argument can be left off completely (in which case the ``['' and ``]'' are also not necessary) and will default to you, the author.  The second argument is required and declares the year of the copyright.  If parts of your thesis were supported by grants or were previously published, you should consult with your advisor and the prior publishers to make sure that you specify these arguments correctly before including this page.

\textbf{Note:} In 2016 (v1.12 of this class file) the Graduate School switched to an electronic thesis submission process and eliminated the Dissertation Acceptance and Library Rights Statement pages which had previously surrounded the Copyright page.  If you are recompiling an older thesis which contains these pages, then you will need to use earlier version of the class file.

\section{University of Maine Graduate School Land Acknowledgment}\label{glsa}
\begin{verbatim}
\glsa{}
\end{verbatim}

This command creates the University of Maine Graduate School Land Acknowledgment. This page is optional and takes no parameters. The land acknowledgment should be after the copyright page, as shown by the thesis template made by the Graduate School. 

\section{Abstract(s)}\label{abstracts}
The graduate requires two abstracts, but only one has to appear in the bound dissertation.

This first abstract is the usual abstract you would write for a scholarly journal in your field.  This is the abstract that must be in the bound thesis.  It should be limited to 500 words for a Master's Thesis and 350 words for a Doctoral Thesis.  It cannot contain formulas, tables, diagrams, or other illustrations.  Typesetting your abstract is accomplished with the ``abstract'' environment:
\begin{verbatim}
\begin{abstract}
...
...
...
\end{abstract}
\end{verbatim}

The second abstract is one suitable for a lay audience.  This abstract is limited to 350 words regardless of the kind of degree you're getting and should not contain highly technical language.  It should be written with the expectation that the reader will have only minimal knowledge of your field as it may be ``submitted [...] for publication in newspapers, magazines, and other media of
interest to the general public, and it may be used in selecting nominees for regional and
national competitions.''  It must be accompanied by at least 5 keywords (for search engines to pick up on, presumably) and it may contain 1 (and only 1) image.  If you didn't create said image, then you need permission of the copyright holder to use it.

This abstract doesn't have to be bound with your thesis, but must be submitted electronically to crystal.burgess@maine.edu.  When submitting this abstract, a Word document that is formated correctly is preferred due to some copy/paste peculiarities between Adobe Reader and the form the grad school uses to upload the file to the web.  If you don't have access to Word, however, you can get away with a pdf version.  This pdf version can be generated by this class file with the ``layabstract'' environment; the same environment you'd use to generate the lay abstract for inclusion in the bound copy:

\begin{verbatim}
\begin{layabstract}{...}
...
...
...
\end{layabstract}
\end{verbatim}

In this case, the environment argument is the list of keywords, while the body of the abstract should be within between the environment commands.  If you do include an image, do not enclose it within a figure environment as it should not appear in the List of Figures.

\section{Dedication}
If there is some person (or group of persons) to whom you want to dedicate your thesis, then you'll need to use the dedication environment.  This should be short, and is optional:
\begin{verbatim}
\begin{dedication}
...
\end{dedication}
\end{verbatim}

\section{Preface}
If you want to include a preface to your thesis then you typeset it with the preface environment.  This can be long or short and is optional.

\begin{verbatim}
\begin{preface}
...
...
...
\end{preface}
\end{verbatim}

\paragraph{Note:}The document structure within the Preface is unnumbered (a Graduate School requirement).

\section{Acknowledgements}
While considered optional by the Graduate School, the acknowledgments are the appropriate place to mention funding sources, collaborators, and anyone who helped with the writing or revision of your thesis.  They are typeset with the acknowledgements environment:

\begin{verbatim}
\begin{acknowledgements}
...
...
...
\end{acknowledgements}
\end{verbatim}

\section{Table of Contents}
The last element of the front matter is the table of contents.  This actually consists of several lists, the first of which is actually called ``Table of Contents'' and contains the name and page numbers of chapters, sections, subsections, and chapter-like elements.  The other lists are all pseudo-optional.  If they would be populated (i.e. if you have tables or figures), then they need to be there.  If they are empty, then you can leave the empty list off.  Typesetting these lists is handled with a series of commands:

\begin{verbatim}
\tableofcontents
\listoftables
\listoffigures
\end{verbatim}

In addition, the Graduate School requires you to have other lists for ``a consistent set of theorems, symbols, abbreviations or definitions'' should such a set appear in your thesis.  Some packages add \verb=\listof*= commands to create and auto-populate the list for the element that they are support just like \verb=\listoftables= and \verb=\listoffigures= do for tables and figures.  If so, you should probably use said command as it will make your life much easier (though pay attention to the formatting that the command creates, you may need to modify it manually).  However, for those instances where the package doesn't do so, there is a ``listof'' environment which you can use to manually create such a page:

\begin{verbatim}
\begin{listof}{...}
...
...
...
\end{listof}
\end{verbatim}

\section{File Close}
The second to last line that should be in your Front file signals the start of the main body of the thesis with the command \verb=\mainmatter=.  This resets the page numbering, changes it to arabic numerals, switches to double spacing, and adds the word ``Chapter'' to your table of contents before your first chapter.

Since this isn't strictly creating a piece of the front matter of your thesis it might seem more logical to put this command in Main.tex after \verb=\include{Front}=, however, this command suffers from the same bug that effects \verb=\references=.  However, since this command comes first in the document, it appears to be subject to it more reliably.  Putting the command at the end of Front.tex dodges that bug (as would placing it at the beginning of Ch1.tex).  It's not elegant, but it works.

The last line of Front.tex is \verb=\endinput=.  This command isn't technically necessary (i.e. your document will typeset just fine without it), but it is good programming practice to include it.  If it is used, then anything that appears after it will be ignored by \LaTeX, making it a great way to create a scratch space at the end of each file where you can write notes to yourself.  You don't even have to comment them out!
\endinput

This is a note to myself which is ignored by LaTeX due to the \endinput command above it.